Identification and analysis of pleiotropic expression quantitative trait loci

### 2023-05-09 doc/presentation_230511_centuriday2023/presentation_centuri2023_marseille.tex
ENH

        \begin{itemize}
            \item Differences between humans coded in 80 x 10$^6$ frequent genetic variants
            \item Genetic variants change susceptibilities for thousands of common traits and diseases
            \item For example, breast cancer:
        \end{itemize}
        %
        \begin{figure}
            \begin{center}
                \includegraphics[width=0.5\textwidth]{\presentationgoldparispath/41586_2017_Article_BFnature24284_Fig1_HTML.jpg}
            \end{center}
            \caption{Genetic variant associations with breast cancer risk (DOI:10.1038/nature24284).}
        \end{figure}

@@

        \begin{itemize}
            \item Large datasets of associations have shown that many genetic variants change simultaneously susceptibility to many diseases, ie. the variants are pleiotropic
        \end{itemize}

@@

        \begin{center}
            \includegraphics[width=0.5\textwidth]{\mspath/plt_x_per_variant_y_egene_distance.py/violin.png}
        \end{center}
        \vfill
        Yes, pleiotropic eQTLs have a lower effect on gene expression and traits

@@

        \begin{itemize}
            \item P Paul
            \item L Lecerf (M1), P Rihet, M Michel, S Marquet, S Spicuglia
        \end{itemize}
%
        \vfill
%
        Funding
%
        \begin{itemize}
            \item Institut Cancer et Immunologie - Aix-Marseille Univ.
            \item Agence nationale de la recherche (ANR)
        \end{itemize}

>>>>

        \begin{itemize}
            \item Differences between humans coded in 80 x 10$^6$ frequent genetic variants
            \item Genetic variants change susceptibilities to thousands of human traits
            \item For example, breast cancer:
        \end{itemize}
        %
        \begin{figure}
            \begin{center}
                \includegraphics[width=0.5\textwidth]{\presentationgoldparispath/41586_2017_Article_BFnature24284_Fig1_HTML.jpg}
            \end{center}
            \caption{Genetic variant associations with breast cancer risk (DOI:10.1038/nature24284).}
        \end{figure}

@@

        \begin{itemize}
            \item Large datasets of associations have shown that many genetic variants change simultaneously susceptibility to many diseases, for instance:
        \end{itemize}

@@

        \begin{figure}[!ht]

            \begin{subfigure}[]{.49\textwidth}
                \textbf{a}
                \\
                \includegraphics[width=\textwidth]{\mspath/pltbar_x_per_gwas_cat_y_beta_neglog10pval.py/eqtl_beta.png}
            \end{subfigure}
            %
            \begin{subfigure}[]{.49\textwidth}
                \textbf{b}
                \\
                \includegraphics[width=\textwidth]{\mspath/pltbar_x_per_gwas_cat_y_beta_neglog10pval.py/gwas_beta.png}
            \end{subfigure}

        \end{figure}
        %
        \vfill
        Yes, pleiotropic eQTLs have a lower effect on gene expression and traits

@@

        \begin{itemize}
            \item P Paul
            \item L Lecerf (M1), P Rihet, M Michel, S Marquet, S Spicuglia
        \end{itemize}
%
        \vfill
%
        Funding
%
        \begin{itemize}
            \item Institut Cancer et Immunologie - Aix-Marseille Univ.
            \item Agence nationale de la recherche (ANR)
            \item Centre de Calcul Intensif d'Aix-Marseille
        \end{itemize}
